Compositional equivalences based on Open pNets

### 2020-04-24 2016-Weak-FH-Bisim/WeakBisim.tex
preuves un peu mises au propre

\begin{proof} ($\Rightarrow$) We proceed by induction on  $n$ and $m$ (where between each step either $m$ or $n$ increases).
\begin{itemize}
\item The base case there is one transition, so $n=-1$ and $m=-1$, we have:
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
 \openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}
%}
\end{mathpar} 
by rule \WTDeux\ we can directly conclude the implication: 
 \begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
% \openrule
%         {
%           \set{\beta},\Pred,\Post}
%         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}

\openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T} \Rightarrow 
{ \openrule
         {
           \vis{\set{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar} 
\item For the inductive step, first we have by induction hypothesis that the formula holds for some lengths $m$ and $n$. Induction step is to infer that formula holds for transitions of length $m+1$ or $n+1$. 
We consider the case $n'=n+1$ (because $m'=m+1$ is similar).  We want to prove (1) $\Rightarrow$ (2) in the lemma, and in (1) we  focus on the case where there is a set of open transitions (this is the case: $s\neq s'$). In other words, we consider the sequence of ($n+m+4$) open transitions: 
\begin{mathpar}
\Big(\forall i \in [0..n+1].\openrule
    {
       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta_2},\Pred_2,\Post_2 }
         {s_2 \OTarrow {\alpha} s'_2} \in \mathcal{T}
\quad \wedge\\
~~\qquad\qquad\forall i \in [0..m].\openrule
         {
           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}
\Big) 
\end{mathpar}

@@

$
%\mprset {vskip=.5ex}
%\inferrule 
\Big(\forall i \in [1..n+1].\openrule
    {
       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T} \,\wedge\,
\openrule
         {
           \set{\beta_2},\Pred_2,\Post_2 }
         {s_2 \OTarrow {\alpha} s'_2} \in \mathcal{T}
\, \wedge\\
{}~~\hspace{2.25cm}\forall i \in [0..m].\openrule
         {
           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}}\! \in\! \mathcal{T}
\Big)  \Rightarrow\!  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s'' \OTWeakarrow {\alpha'} s'} \in\WT
}
$
where\\
$
\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\!\!\Post_{1j}}}\\
s''=s_{10} \wedge s_{1(n+2)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
\displaystyle{
\set{\gamma}=\mybigdotcup_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup}\\
{}~\qquad \displaystyle{\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
\\
\Pred=\bigwedge_{i=1}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{1}\Post_{1j}}\land\\ 
{}~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}}\Big)\\
\Post=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}
$

@@

\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
       {
           \vis{\set{\beta_{10}}}\!,\Pred_{10},\Post_{10}
				 } {s_{10} \OTWeakarrow {\tau}s_{11}}\! \in\! \WT
\quad
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s'' \OTWeakarrow {\alpha'} s'}\! \in\!\WT
\quad
\openrule
         {
          \emptyset,\True,\Id(s'')
				 } {s' \OTWeakarrow {\tau} s'}\! \in\! \WT
\\
\set{\gamma''}= \vis{\set{\beta_{10}}} \dotcup \set{\gamma}\subst{\Post_{10}}\quad
\Pred\,''=\Pred_{10}\land\Pred\subst{\Post_{10}}\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_{10}}
\Post\,''=\Id(s'')\shortotimes\Post\shortotimes\Post_{10} \quad \alpha''=\alpha'\subst{\Post_{10}}
}
{
\openrule
         {
          \set{\gamma''}, \Pred\,'',\Post\,''
				 } 
         {s_{10} \OTWeakarrow {\alpha''} s'} \in\!\WT
} \WTTrois
\end{mathpar}
where we obtain the conclusion of the lemma, as required with the following assertions (derived from previous assertions):
\begin{gather*}
s_{10}=s_{10} \wedge s_{1(n+2)}=s_{2} \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
\begin{align*}
\alpha''=&\alpha\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}\subst{\Post_{10}} = \alpha\subst{\bigotimes_{j=n+1}^{0}\Post_{1j}}\\
\set{\gamma''}=&\mybigdotcup_{i=0}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup\\
&\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }
\\
\Pred=&\bigwedge_{i=0}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{0}\Post_{1j}}\land\\ 
&\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{0}\Post_{1j}}\Big)
\\
\Post=&\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{0}\Post_{1j}
\end{align*}
\end{gather*}

@@

\item Similarly, a series of $m_1$ open transitions such that $m_1=n+m+3$   can be simplified as follows: 
\begin{mathpar}
%\inferrule{
\openrule
         {
           \set{\gamma_3},\Pred_3,\Post_3   }
         {s'' \OTWeakarrow {\tau} s'''} \in\! \WT
\Rightarrow\, 
\forall i \in [0..m_1].\openrule
    {
       \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}        
\end{mathpar}
where\\
$ 
s''=s_{30} \wedge s_{3{(m_1+1)}}\!=s''',\quad
\displaystyle{\set{\gamma_3}= \mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{3 i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{3 j} } }} \\
\Pred_3\!=\!\bigwedge_{i=0}^{m_1}(\Pred_{3i} \subst{\bigotimes_{j=i-1}^{0}\Post_{3 j}} ),\quad \Post_3= \bigotimes_{i=m_1}^{0} \subst{\Post_{3i}} 
$

@@

\openrule
         {
           \set{\beta'},\Pred\,',\Post\,' }
         {s_2 \OTarrow {\alpha''} s_2'} \in \mathcal{T}
 \wedge
\forall i \in [0..m_2].\openrule
         {
           \set{\beta_{2i}'},\Pred_{2i}^{\,\prime},\Post'_{2i}    }
         {s_{2i}' \OTarrow {\tau} s_{2(i+1)}'} \in \mathcal{T}
\bigg)         
\end{mathpar}
where
\begin{gather*}
s'=s_{20} \wedge s_{2(n_2+1)}=s_2 \wedge  s_2' = s_{20}' \wedge s_{2(m_2+1)}'=s''\\
\begin{align*}
\alpha''=&\alpha'\subst{\bigotimes_{j=n_2}^{0}\Post_{2j}}\\
\set{\gamma_2}=&\mybigdotcup_{i=0}^{n_2} \vis{\set{\beta_{2i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{2 j} } }  \dotcup  \vis{\set{\beta'}\subst{\bigotimes_{j=n_2}^{0}\Post_{2j}}} \dotcup\\
&
 \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{2i}} \subst{\bigotimes_{j=i-1}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j=n_2}^{0}\Post_{2j}}}
\\
\Pred_2=&\bigwedge_{i=0}^{n_2}\Pred_{2i}\subst{\bigotimes_{j=i-1}^{0}\Post_{2j}}\land\Pred\,' \subst{\bigotimes_{j={n_2}}^{0}\Post_{2j}}\land\\ 
&\Big(\bigwedge_{i=0}^{m_2}\Pred\,'_{2i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}}\Big)\\
\Post_2=\bigotimes_{j=m_2}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}
\end{align*}
\end{gather*}

@@

such that\\
\begin{align*}
s_{4i}=\begin{cases}
			s_{1i} & \mbox{if }i<n_1\\
			s_{2i-n_1} & \mbox{if }i\geq n_1
	   \end{cases}
&\qquad\qquad\qquad&
s_{5i}=\begin{cases}
			s_{3i} & \mbox{if }i<m_1\\
s_{2i-m_1}' & \mbox{if }i\geq m_1
	\end{cases}\\
\end{align*}

@@

Also, we have the following assertions:\\
$
{\displaystyle \alpha''=\alpha\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}\!}\\
s\!=\!s_{40} \wedge s_{4(n_1+n_2+1)}\!=s_2 \wedge s_2' = s_{50} \wedge s_{5(m_1+m_2+1)}\!=\!s'\\
\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2} \vis{\set{\beta_{4i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{4 j} } }  \dotcup  \vis{\set{\beta'}\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}}\dotcup }\\
{}~\!\qquad\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{5i}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4i}} }
\\
\displaystyle{\Pred=
\bigwedge_{i=0}^{n_1+n_2}\!\!\Pred_{4i}\subst{\bigotimes_{j=i-1}^{0}\Post_{4j}}\land\Pred\,' \subst{\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\land}\\ 
{}~\qquad\quad\bigwedge_{i=0}^{m_1+m_2}\Pred_{5i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{5j}\shortotimes\Post\,'\shortotimes\!\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\\
\Post=\bigotimes_{j=m_1+m_2}^{0}\!\!\!\Post_{5j}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\Post_{4j}
$\\
This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible with the right side conditions. 
\end{itemize}
\end{proof}

>>>>

\begin{proof} ($\Rightarrow$) We present an induction on $n$ and $m$, focusing on the incrementation on $n$: we prove that the property is valid for $-1$, $-1$ prove a general induction for going from $n$ to $n+1$, a similar induction can be applied to go from $m$ to $m+1$
\begin{itemize}
\item The base case there is one transition, so $n=-1$ and $m=-1$, we have:
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
 \openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}
%}
\end{mathpar} 
by rule \WTDeux\ we can directly conclude the implication: 
 \begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
% \openrule
%         {
%           \set{\beta},\Pred,\Post}
%         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}

\openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T} \Rightarrow 
{ \openrule
         {
           \vis{\set{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar} 
\item For the inductive step, first we have by induction hypothesis that the formula holds for some lengths $m$ and $n$. Induction step is to infer that formula holds for transitions of length  $n+1$. 
We consider the case $n'=n+1$.  We want to prove (1) $\Rightarrow$ (2) in the lemma, and in (1) we  focus on the case where there is a set of open transitions (this is the case: $s\neq s'$). In other words, we consider the sequence of ($n+m+4$) open transitions: 
\begin{mathpar}
\Big(\forall i \in [0..n+1].\openrule
    {
       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta_2},\Pred_2,\Post_2 }
         {s_2 \OTarrow {\alpha} s'_2} \in \mathcal{T}
\quad \wedge\\
~~\qquad\qquad\forall i \in [0..m].\openrule
         {
           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}
\Big) 
\end{mathpar}

@@

$
%\mprset {vskip=.5ex}
%\inferrule 
\Big(\forall i \in [1..n+1].\openrule
    {
       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T} \,\wedge\,
\openrule
         {
           \set{\beta_2},\Pred_2,\Post_2 }
         {s_2 \OTarrow {\alpha} s'_2} \in \mathcal{T}
\, \wedge\\
{}~~\hspace{2.25cm}\forall i \in [0..m].\openrule
         {
           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}}\! \in\! \mathcal{T}
\Big)  \Rightarrow\!  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s'' \OTWeakarrow {\alpha'} s'} \in\WT
}
$
where\\
\begin{align*}
s''=s_{10} &\wedge s_{1(n+2)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
\alpha'=&\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\!\!\Post_{1j}}}\\
\set{\gamma}=&\mybigdotcup_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup\\
& \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }\\
\Pred=&\bigwedge_{i=1}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{1}\Post_{1j}}\land\\ 
&\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}}\Big)\\
\Post=&\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}
\end{align*}

@@

\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
       {
           \vis{\set{\beta_{10}}}\!,\Pred_{10},\Post_{10}
				 } {s_{10} \OTWeakarrow {\tau}s_{11}}\! \in\! \WT
\quad
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s'' \OTWeakarrow {\alpha'} s'}\! \in\!\WT
\quad
\openrule
         {
          \emptyset,\True,\Id(s'')
				 } {s' \OTWeakarrow {\tau} s'}\! \in\! \WT
\\
\set{\gamma''}= \vis{\set{\beta_{10}}} \dotcup \set{\gamma}\subst{\Post_{10}}\quad
\Pred\,''=\Pred_{10}\land\Pred\subst{\Post_{10}}\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_{10}}
\Post\,''=\Id(s'')\shortotimes\Post\shortotimes\Post_{10} \quad \alpha''=\alpha'\subst{\Post_{10}}
}
{
\openrule
         {
          \set{\gamma''}, \Pred\,'',\Post\,''
				 } 
         {s_{10} \OTWeakarrow {\alpha''} s'} \in\!\WT
} \WTTrois
\end{mathpar}
where we obtain the conclusion of the lemma, as required with the following assertions (derived from previous assertions):
\begin{align*}
s_{10}=s_{10} &\wedge s_{1(n+2)}=s_{2} \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
\alpha''=&\alpha\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}\subst{\Post_{10}} = \alpha\subst{\bigotimes_{j=n+1}^{0}\Post_{1j}}\\
\set{\gamma''}=&\mybigdotcup_{i=0}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup\\
&\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }
\\
\Pred=&\bigwedge_{i=0}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{0}\Post_{1j}}\land\\ 
&\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{0}\Post_{1j}}\Big)
\\
\Post=&\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{0}\Post_{1j}
\end{align*}

@@

\item Similarly, a series of $m_1$ open transitions such that $m_1=n+m+3$   can be simplified as follows: 
\begin{mathpar}
%\inferrule{
\openrule
         {
           \set{\gamma_3},\Pred_3,\Post_3   }
         {s'' \OTWeakarrow {\tau} s'''} \in\! \WT
\Rightarrow\, 
\forall i \in [0..m_1].\openrule
    {
       \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}        
\end{mathpar}
where
\begin{mathpar}
s''=s_{30}

\land

 s_{3{(m_1+1)}}\!=s'''

\land

\displaystyle{\set{\gamma_3}= \mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{3 i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{3 j} } }}

\land

\Pred_3\!=\!\bigwedge_{i=0}^{m_1}(\Pred_{3i} \subst{\bigotimes_{j=i-1}^{0}\Post_{3 j}} )

\land

 \Post_3= \bigotimes_{i=m_1}^{0} \subst{\Post_{3i}} 
\end{mathpar}

@@

\openrule
         {
           \set{\beta'},\Pred\,',\Post\,' }
         {s_2 \OTarrow {\alpha''} s_2'} \in \mathcal{T}
 \wedge
\forall i \in [0..m_2].\openrule
         {
           \set{\beta_{2i}'},\Pred_{2i}^{\,\prime},\Post'_{2i}    }
         {s_{2i}' \OTarrow {\tau} s_{2(i+1)}'} \in \mathcal{T}
\bigg)         
\end{mathpar}

where
\begin{align*}
s'=s_{20} &\wedge s_{2(n_2+1)}=s_2 \wedge  s_2' = s_{20}' \wedge s_{2(m_2+1)}'=s''\\
\alpha''=&\alpha'\subst{\bigotimes_{j=n_2}^{0}\Post_{2j}}\\
\set{\gamma_2}=&\mybigdotcup_{i=0}^{n_2} \vis{\set{\beta_{2i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{2 j} } }  \dotcup  \vis{\set{\beta'}\subst{\bigotimes_{j=n_2}^{0}\Post_{2j}}} \dotcup\\
&
 \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{2i}} \subst{\bigotimes_{j=i-1}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j=n_2}^{0}\Post_{2j}}}
\\
\Pred_2=&\bigwedge_{i=0}^{n_2}\Pred_{2i}\subst{\bigotimes_{j=i-1}^{0}\Post_{2j}}\land\Pred\,' \subst{\bigotimes_{j={n_2}}^{0}\Post_{2j}}\land\\ 
&\Big(\bigwedge_{i=0}^{m_2}\Pred\,'_{2i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}}\Big)\\
\Post_2=&\bigotimes_{j=m_2}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}
\end{align*}

@@

such that
\begin{align*}
s_{4i}=\begin{cases}
			s_{1i} & \mbox{if }i<n_1\\
			s_{2i-n_1} & \mbox{if }i\geq n_1
	   \end{cases}
&\qquad\qquad\qquad&
s_{5i}=\begin{cases}
			s_{3i} & \mbox{if }i<m_1\\
s_{2i-m_1}' & \mbox{if }i\geq m_1
	\end{cases}\\
\end{align*}

@@

Also, we have the following assertions:
\begin{align*}
s\!=\!s_{40}& \wedge s_{4(n_1+n_2+1)}\!=s_2 \wedge s_2' = s_{50} \wedge s_{5(m_1+m_2+1)}\!=\!s'\\
\alpha''=&\alpha\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}\\
\set{\gamma}=&\mybigdotcup_{i=0}^{n_1+n_2} \vis{\set{\beta_{4i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{4 j} } }  \dotcup  \vis{\set{\beta'}\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}}\dotcup \\
&\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{5i}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4i}} }\\
\Pred=&
\bigwedge_{i=0}^{n_1+n_2}\!\!\Pred_{4i}\subst{\bigotimes_{j=i-1}^{0}\Post_{4j}}\land\Pred\,' \subst{\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\land\\ 
&\quad\bigwedge_{i=0}^{m_1+m_2}\Pred_{5i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{5j}\shortotimes\Post\,'\shortotimes\!\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\\
\Post=&\bigotimes_{j=m_1+m_2}^{0}\!\!\!\Post_{5j}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\Post_{4j}
\end{align*}

This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible with the right side conditions. 
\end{itemize}
\end{proof}
